---
title: "Inferential statistics (LME) and Figure 3"
author: "Jason Lo"
date: "20210806"
output:
  html_document:
    df_print: paged
    theme: united
---

# Analyses {.tabset}

## Imports
```{r, message=FALSE, warning=FALSE}
source("helper.R")

df_growth_parameters <- read.csv('../../data/growth_params_1250.csv') %>%
    mutate(growth = log(k + 1)) %>%
    gather("Measure", "Score",
        mse, max_acc, growth, k, x0) %>% 
    mutate(Lexicality = ifelse(cond %in% c("NW_AMB", "NW_UN"), "Nonword", "Word")) %>% 
    mutate(Lexicality = factor(Lexicality, levels=c("Word", "Nonword")))

# Asymptote df
dfa <- df_growth_parameters %>% 
    filter(Measure == "max_acc") %>%
    droplevels() %>% 
    mutate(scaled_p_noise = scale(p_noise)) %>% 
    mutate(scaled_hidden_units = scale(hidden_units)) %>% 
    mutate(scaled_learning_rate = scale(learning_rate))

# Growth df
dfg <- df_growth_parameters %>% 
    filter(Measure == "growth") %>%
    droplevels() %>% 
    mutate(scaled_p_noise = scale(p_noise)) %>% 
    mutate(scaled_hidden_units = scale(hidden_units)) %>% 
    mutate(scaled_learning_rate = scale(learning_rate))
```

## Lexicality effect on growth parameters

### Asymptote
```{r}
my_lmer("Score ~ Lexicality", dfa)
```

### Growth
```{r}
my_lmer("Score ~ Lexicality", dfg)
```

## Table 1
The Effects of Control Parameters on Word and Nonword asymptote  

Import data for table 1
```{r}
# Word asymptote
dfa_word <- dfa %>% filter(Lexicality == "Word")

# Nonword asymptote
dfa_nonword <- dfa %>% filter(Lexicality == "Nonword")

```

### Word
```{r}
my_lmer("Score ~ scaled_p_noise * scaled_hidden_units * scaled_learning_rate", dfa_word)
```

### Nonword
```{r}
my_lmer("Score ~ scaled_p_noise * scaled_hidden_units * scaled_learning_rate", dfa_nonword)
```





## Table 2
The Effect of Control Parameters on Word and Nonword Growth Parameter 

Import data for table 2
```{r}
# Word growth rate
dfg_word <- dfg %>% filter(Lexicality == "Word")

# Nonword growth rate
dfg_nonword <- dfg %>% filter(Lexicality == "Nonword")
```

### Word
```{r}
my_lmer("Score ~ scaled_p_noise * scaled_hidden_units * scaled_learning_rate", dfg_word)
```

### Nonword
```{r}
my_lmer("Score ~ scaled_p_noise * scaled_hidden_units * scaled_learning_rate", dfg_nonword)
```


## Figure 3

```{r}
fig3_model <- lmer("Score ~ p_noise * hidden_units * learning_rate * Lexicality + (1|code_name)", dfg)
interaction_plots <- plot_model(fig3_model, type="int")

fig3 <- interaction_plots[8][[1]] + 
  labs(x="P-Noise", y="Growth Paramerter") +
  ggtitle("")+
  theme_minimal()

ggsave("../../results/figure3.jpg", width = 5, height=3, dpi=600)
```

## Supplementary statistics

Import data for supplementary table 1
```{r}
df_eot <- read.csv('../../data/data_part1_1250.csv') %>%
    rename(code_name = ID,
           epoch = Trial.Scaled,
           hidden_units = Hidden,
           p_noise = Pnoise,
           learning_rate = Epsilon,
           cond = Type) %>% 
    filter(Measure == "Accuracy") %>% 
    filter(epoch == 1.0) %>% 
    mutate(Lexicality = ifelse(cond %in% c("NW_AMB", "NW_UN"), "Nonword", "Word")) %>% 
    mutate(scaled_p_noise = scale(p_noise)) %>% 
    mutate(scaled_hidden_units = scale(hidden_units)) %>% 
    mutate(scaled_learning_rate = scale(learning_rate))

df_eot_word <- df_eot %>% filter(Lexicality == "Word")
df_eot_nonword <- df_eot %>% filter(Lexicality == "Nonword")
```

### Frequency by consistency effect at the end of training
```{r}
my_lmer("Score ~ Freq * Cons", df_eot_word)
```

Consistency effect in low frequency words
```{r}
my_lmer("Score ~ Cons", filter(df_eot_word, Freq=="LF"))
```
Consistency effect in high frequency words
```{r}
my_lmer("Score ~ Cons", filter(df_eot_word, Freq=="HF"))
```
### Lexicality effect
```{r}
my_lmer("Score ~ Lexicality", df_eot)
```



## Supplementary table 1

Lexicality
```{r}
my_lmer("Score ~ Lexicality")
```



### Word
```{r}
my_lmer("Score ~ scaled_p_noise * scaled_hidden_units * scaled_learning_rate", df_eot_word)
```

### Nonword
```{r}
my_lmer("Score ~ scaled_p_noise * scaled_hidden_units * scaled_learning_rate", df_eot_nonword)
```
